Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-01-19 minimax.tex
some wording

Let us also mention works addressing the manipulability of voting rules \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011,Baumeister2019}, and studies of strategic behaviors
% when agents learn incrementally about other agent preferences
 \citep{Endriss2016,Lev2019,Annemieke2012}.

Our approach is evaluated in simulations where both the voting rule and the agent's preferences are initially unknown to the system and incrementally revealed by answering questions.
We compare the effectiveness of several strategies of choosing questions depending on the current knowledge.
In this work:
\begin{itemize}
	\item we provide a novel mechanism for elicitating a voting rule by translating abstract questions about weights to direct choice questions about a profile;  
	\item we show that in small problem sizes, starting with zero knowledge, it is possible to reach a low regret level with a reasonable number of questions;
	\item we present elicitation strategies that achieve good results within reasonable computation time for small problem sizes;
	\item we show that for the class of rule considered, asking a few questions about the voting rule suffice to reach a low regret level;
	\item our experiments suggest that low degree of similarity among preference rankings (like in the case of impartial culture) is a more challenging setting than less varied profiles.
\end{itemize}

@@

As part of our contribution, a general open-source library, allowing to reproduce our experiments and perform many more, will be made publicly available (URL not displayed for ensuring anonymity).
%and serve as a basis for further research

>>>>

We also mention works addressing the manipulability of voting rules \citep{Elkind2012,Dey2018,Dey2018_2,Conitzer2011,Baumeister2019} and 
strategic behaviors \citep{Endriss2016,Lev2019,Annemieke2012}.

Our approach is evaluated in simulations where both the voting rule and the agent's preferences are initially unknown to the system and incrementally revealed by answering questions.
We compare the effectiveness of several question strategies based on the current knowledge about the rule and preferences.
To summarize:
\begin{itemize}
	\item we provide a novel mechanism for eliciting a voting rule by translating abstract questions about weights to a choice of an alternative given a concrete profile;  
	\item we show that in small problem sizes, %starting with zero knowledge,
	 it is possible to reach a low regret level with a reasonable number of questions;
	\item we present elicitation strategies that achieve good results within reasonable computation time for small problem sizes;
	\item we show that for the class of rule considered, asking a few questions about the voting rule suffice to reach a low regret level;
	\item our experiments suggest that low degree of similarity among preferences %rankings 
	(as in impartial culture) is a more challenging setting than less varied profiles.
\end{itemize}

@@

As part of our contribution, a general open-source library, allowing to reproduce our experiments and perform many more, will be made publicly available.\footnote{URL not displayed for ensuring anonymity.}
%and serve as a basis for further research
